The \dealii{} Library, Version 9.3

### 2021-06-18 9.3/paper.tex
Remove Bruno Blais from the "other contributors".

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%
% 9.3: updated 5/08/2021 PM
%      sorted by WB 5/28
Pasquale Africa,
Tyler Anderson,
Mathias Anselmann,
Arpit Babbar,
Maximilian Bergbauer,
Nicolas Barnafi,
Bruno Blais,
Michele Bucelli,
Marcus Calhoun-Lopez,
Fabian Castelli, %He provided major contributions to candi for v9.3
Praveen Chandrashekar,
Conrad Clevenger,
David F. Castellanos,
Andrew Davis,
Elias Dejene,
Niklas Fehn,
Menno Fraters,
Ivan Fumagalli,
Daniel Garcia-Sanchez,
Nicola Giuliani,
Krishnakumar Gopalakrishnan,
Alexander Grayver,
Olivier Guevremont,
Jake Harmon,
Graham Harper,
Katharina Kormann,
Christoph Kammer,
Wenyu Lei,
Zhou Lei,
Phillip Mobley,
Nils Much,
Pratik Nayak,
Toni El Geitani Nehme,
Justin O'Connor,
Daniel Paukner,
Lei Qiao,
Ce Qin,
Reza Rastak,
Julian Roth,
Laura Prieto Saavedra,
Doug Shi-Dong,
David Schneider,
Magdalena Schreter,
Richard Schussnig,
Dominic Soldner,
Simon Sticko,
Malhar Tidke,
Ignacio Tomas,
Peter Westerbaan.

\todo[inline]{Remove everyone who may end up being a co-author.}

>>>>

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%
% 9.3: updated 5/08/2021 PM
%      sorted by WB 5/28
Pasquale Africa,
Tyler Anderson,
Mathias Anselmann,
Arpit Babbar,
Maximilian Bergbauer,
Nicolas Barnafi,
Michele Bucelli,
Marcus Calhoun-Lopez,
Fabian Castelli, %He provided major contributions to candi for v9.3
Praveen Chandrashekar,
Conrad Clevenger,
David F. Castellanos,
Andrew Davis,
Elias Dejene,
Niklas Fehn,
Menno Fraters,
Ivan Fumagalli,
Daniel Garcia-Sanchez,
Nicola Giuliani,
Krishnakumar Gopalakrishnan,
Alexander Grayver,
Olivier Guevremont,
Jake Harmon,
Graham Harper,
Katharina Kormann,
Christoph Kammer,
Wenyu Lei,
Zhou Lei,
Phillip Mobley,
Nils Much,
Pratik Nayak,
Toni El Geitani Nehme,
Justin O'Connor,
Daniel Paukner,
Lei Qiao,
Ce Qin,
Reza Rastak,
Julian Roth,
Laura Prieto Saavedra,
Doug Shi-Dong,
David Schneider,
Magdalena Schreter,
Richard Schussnig,
Dominic Soldner,
Simon Sticko,
Malhar Tidke,
Ignacio Tomas,
Peter Westerbaan.
